Neural Neural Textures Make Sim2Real Consistent

### 2022-06-24 CORL/appendix.tex
Added robot arm animation

		We have created animations using TRITON to see how consistency helps:

		https://youtu.be/fuTSta_M6NQ

>>>>

		In this section we have links to animations that help demonstrate various aspects of TRITON.
		If you are viewing this document on a computer, click a thumbnail to view the video.

		% https://youtu.be/fuTSta_M6NQ

		\begin{figure}[H]
			\begin{center}
			\href{https://youtu.be/kecK_cJgLT8}{
					\includegraphics[width=400pt]{../images/robot_arm_animation_thumbnail.png}
					}
				\end{center}
			\caption{
				This animation shows a side-by-side comparision of different camera viewpoints of the results discussed in section \ref{sec:robotarm_results}, as well as the inputs, ground truth video, TRITON and TRITON ablation videos.
				Url: \href{https://youtu.be/kecK_cJgLT8}{youtu.be/kecK\_cJgLT8}
			}
			\label{fig:robotarm_anim}
		\end{figure}
